---
title: "CES_analysis_Final"
author: "Jackson"
date: "2023-07-14"
output: html_document
---

#### Load in Libraries

```{r,message=FALSE, warning=FALSE}
library(tidyverse)
library(visdat)
library(lavaan)
library(psych)
library(corrplot)
library(stargazer)
library(margins)
library(mfx)
```

#### Load in data

```{r}
if (file.exists("/Users/jackson/Desktop/Thesis/Data/CES20_Common_OUTPUT_vv.csv")) { ## for me :)
  data <- read_csv("/Users/jackson/Desktop/Thesis/Data/CES20_Common_OUTPUT_vv.csv")
} else {
  data <- read_csv("https://dataverse.harvard.edu/api/access/datafile/4949558") # WARNING: 188mb download.
} 
```

### Transform data 

Relevant variables subsetted from CES 2020 dataset, and re-coded/ to mirror variable specification from Ansolabehere and Hersh 2012. 
```{r}
data_2 <- data %>% 
  dplyr::select(
         caseid, 
         CL_2020gvm, #did you actually vote (validated)? - yes if 1-4, no if 5
         CC20_401, #did you vote? - yes if 5, no otherwise (post)
         CC20_363, #vote intention - 1 = yes definitely, 2 = probably, 3 = I already voted, 4 = I plan to vote before Nov 3rd, 5 = no, 6 = undecided
                      # Did you...
         CC20_300_1,  # use social media in the last 24h?
         CC20_300d_1, # post story link or video about politics?
         CC20_300d_2, # post comment about politics?
         CC20_300d_3, # read a story or watched video about politics?
         CC20_300d_4, # follow a political event?
         CC20_300d_5, # forward a story video photo or link about politics to friend?
         CC20_300d_6, # none of the above
         birthyr,
         gender,
         educ,
         race,
         marstat, #marital status
         faminc_new,#family annual income over past yr
         pew_churatd, #church attendance
         newsint, #political interest
         ideo5, #ideology 1 - very liberal, 2 - liberal, 3 - moderate, 4 - conservative, 5 - very conservative, 6 - don't know
         pid7, # 7 point party ID
         commonweight,
         commonpostweight
         ) %>% 

  mutate(
    
    #Did you plan to vote? Did you vote?
    intend_to_vote = ifelse(CC20_363 %in% c(1,4), 1, 0),
    did_you_vote = ifelse(CC20_401 == 5, 1, 0),
    validated_vote = ifelse(CL_2020gvm == 5, 0, 1),
    over_reported_intention = ifelse(intend_to_vote == 1 , 1, 0),
    over_reported_vote = ifelse(did_you_vote == 1, 1, 0),
    
    #Social media usage
    posted_story_link = ifelse(CC20_300d_1 == 2, 0, 1),
    posted_comment = ifelse(CC20_300d_2 == 2, 0, 1),
    saw_story = ifelse(CC20_300d_3 == 2, 0, 1),
    followed_political_event = ifelse(CC20_300d_4 == 2, 0, 1),
    forwarded_story = ifelse(CC20_300d_5 == 2, 0, 1),
    
    # To what degree have you been politically engaged (gross)?
    social_media_engagement = posted_story_link + posted_comment + saw_story + followed_political_event + forwarded_story,
    
     # Have you been politically engaged on social media within the past day?
    is_politically_engaged = ifelse(social_media_engagement >= 1, 1, 0),
    
    #What kind of user are you?
    active_user = ifelse(posted_comment == 1 | posted_story_link == 1 | followed_political_event == 1, 1, 0),

    passive_user = ifelse((posted_comment == 0 & posted_story_link == 0 & forwarded_story == 0) &
                      (saw_story == 1 | followed_political_event == 1), 1, 0),

    
    #Education
    education = case_when(
      educ == 1 ~ 0,
      educ == 2 ~ 1,
      educ %in% c(3, 4) ~ 2,
      educ == 5 ~ 3,
      educ == 6 ~ 4
    ),
    
    #Household Income
    income = case_when(
      faminc_new %in% c(1, 2, 3) ~ 1,
      faminc_new %in% c(4, 5) ~ 2,
      faminc_new %in% c(6, 7, 8, 9) ~ 3,
      faminc_new %in% c(10, 11, 12, 13, 14, 16) ~ 4,
      faminc_new == 97 ~ 5
    ),
    
    #Church attendance
    church_attendance = case_when(
      pew_churatd == 6 ~ 0,
      pew_churatd %in% c(4, 5) ~ 1,
      pew_churatd == 3 ~ 2,
      pew_churatd %in% c(1, 2) ~ 3,
      pew_churatd == 7 ~ 4),

    #Age
    age = 2020 - birthyr,
    age_cat = cut(age,
                  
                  breaks = c(17, 24, 34, 44, 54, Inf),
                  labels = c("1", "2", "3", "4", "5"), #18-24, 25-44, 45-54, 55 and over
                  right = TRUE, include.lowest = TRUE),
    
    #Ideological strength
    ideological_strength = case_when(
      ideo5 %in% c(3, 6) ~ 0,
      ideo5 %in% c(2, 4) ~ 1,
      ideo5 %in% c(1, 5) ~ 2
      ),

    #Political interest
    political_interest = case_when(
      newsint %in% c(7, 4) ~ 0,
      newsint == 3 ~ 1,
      newsint == 2 ~ 2,
      newsint == 1 ~ 3
    ),
    
    #Partisan strength
    partisan_strength = case_when(
      pid7 %in% c(4, 8) ~ 0,
      pid7 %in% c(3, 5) ~ 1,
      pid7 %in% c(2, 6) ~ 2,
      pid7 %in% c(1, 7) ~ 3
      ),
   
    
    #Female
    female = ifelse(gender == 2, 1, 0),

    #Race
    White = ifelse(race == 1, 1, 0),
    Black = ifelse(race == 2, 1, 0),
    other_non_White = ifelse(!race %in% c(1, 2), 1, 0),
    
    #Married
    married = ifelse(marstat == 1, 1, 0),
      
    )
```




#### Visualize missing data 

```{r}
vis_miss(data_2, warn_large_data = F)

  ### Subset of solely over-reporters (intention)
overreported <- data_2 %>% 
  filter(validated_vote == 0 & intend_to_vote == 1 & !is.na(CL_2020gvm))
```




#### Delete rows with NA values in key variables.

```{r}
nonvoters <- data_2 %>% 
  filter(CL_2020gvm == 5  & complete.cases(CC20_300d_6, CC20_363, CC20_401))
```




#### Create user engagement categories - either active/passive 

```{r}
### 50th percentile engagement score

nonvoters <- nonvoters %>% 
  mutate(user_engagement_score = saw_story + 
           2*followed_political_event + 
           3*forwarded_story + 3*posted_comment + 
           4*posted_story_link,
         
         #If user is in bottom 50th percentile then passive, otherwise active
         user_engagement_category = ifelse(user_engagement_score >= quantile(user_engagement_score, 0.5, na.rm=T), 0, 1)
         )
```




#### Confirmatory Factor Analysis

```{r}
cfa <- 'latent_social_media_engagement =~ posted_story_link + posted_comment + saw_story + followed_political_event + forwarded_story'
fit<- cfa(cfa, data=nonvoters)
summary(fit, fit.measures=T)

### All variables are positive indicators of social media engagement

alpha(nonvoters[, c("posted_story_link", "posted_comment", "saw_story", "followed_political_event", "forwarded_story")])

### Raw alphas range from ~0.66-0.72 indicating stable internal consistency.
```



#### Descriptive Statistics Tables

```{r}
categorical_vars <- list("is_politically_engaged",
                         "social_media_engagement",
                         "passive_user",
                         "user_engagement_category",
                         "ideo5",
                         "education",
                         "income",
                         "Black",
                         "other_non_White",
                         "married",
                         "church_attendance",
                         "age_cat",
                         "ideological_strength",
                         "female",
                         "political_interest")

get_stats <- function(data, var) {
  data %>%
    count(.data[[var]]) %>%
    mutate(
      proportion = n / sum(n) * 100,
      cumulative_freq = cumsum(proportion)
    )
}

stats_list <- lapply(categorical_vars, function(var) get_stats(nonvoters, var))

stats_list

```




#### Proportion of over-reporters by category

```{r}
summarize_overreporters <- function(nonvoters, category) {
  nonvoters %>%
    group_by({{ category }}) %>% 
    summarize(count = n(),
              overreport = sum(over_reported_intention, na.rm = TRUE),
              prop = overreport / count)
}

prop_overreporters <- lapply(categorical_vars, function(cat) {
  summarize_overreporters(nonvoters, !!sym(cat))
})

prop_overreporters
```





#### Proportion of over-reporters by social media engagement figure

```{r}
generate_proportions_fig <- function(data, group_col, x_label, title) {
  data %>% 
    group_by(!!sym(group_col), over_reported_intention) %>%
    summarize(count = n(), .groups = "drop") %>%
    mutate(over_reported_intention = ifelse(over_reported_intention == 1, "Yes", "No")) %>%
    mutate(over_reported_intention = factor(over_reported_intention, levels = c("No", "Yes"))) %>%
    group_by(!!sym(group_col)) %>%
    mutate(proportion = count / sum(count)) %>%
    ungroup() %>%
    
    ggplot(aes(x = !!sym(group_col), y = proportion, fill = over_reported_intention)) +
    geom_bar(stat = "identity", position = "stack") +
    scale_fill_grey(name = "Over-reported vote") +
    xlab(x_label) +
    ylab("Proportion") +
    theme_minimal() +
    ggtitle(title)
}

is_politically_engaged_proportions <- generate_proportions_fig(nonvoters, 
                                     "is_politically_engaged", 
                                     "Is politically engaged?", 
                                     "Proportion of Over-report by Political Engagement on Social Media")
is_politically_engaged_proportions

user_engagement_proportions <- generate_proportions_fig(nonvoters, 
                                  "user_engagement_category", 
                                  "User Engagement Category", 
                                  "Proportion of Over-report by User Engagement")
user_engagement_proportions

sme_proportions <- generate_proportions_fig(nonvoters, 
                  "social_media_engagement", 
                  "Social Media Engagement", 
                  "Proportion of Over-report by Social Media Engagement")
sme_proportions

ideo_proportions <- generate_proportions_fig(nonvoters, 
                   "ideo5", 
                   "Ideology", 
                   "Proportion of Over-report by Ideology")
ideo_proportions

```


```{r}
over_report_ideo <- nonvoters %>%
  
  mutate(over_reported_intention = factor(over_reported_intention, levels = c(0, 1), labels = c("No", "Yes"))) %>%
  
  mutate(ideo_label = case_when(
    ideo5 == 1 ~ "Very Liberal",
    ideo5 == 2 ~ "Liberal",
    ideo5 == 3 ~ "Moderate",
    ideo5 == 4 ~ "Conservative",
    ideo5 == 5 ~ "Very Conservative",
    ideo5 == 6 ~ "Don't know"
  ))%>% 
  mutate(ideo_label = factor(ideo_label, levels = c("Very Liberal", "Liberal", "Moderate", "Conservative", "Very Conservative", "Don't know"))) %>%
  
  ggplot(aes(x = ideo_label, fill = over_reported_intention)) +
  geom_bar(position = "stack") +
  labs(x = "Ideology", y = "Count", fill = "Over Reported Vote") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Proportion of over-reports among nonvoters by ideology")
over_report_ideo

over_report_engaged <- nonvoters %>% 
  mutate(over_reported_intention = factor(over_reported_intention, levels = c(0, 1), labels = c("No", "Yes"))) %>%
  mutate(engaged_label = case_when(
    is_politically_engaged == 1 ~ "Yes",
    is_politically_engaged == 0 ~ "No"
  )) %>% 
  mutate(engaged_lable = factor(engaged_label, levels = c("No", "Yes"))) %>%
  
  ggplot(aes(engaged_label, fill=over_reported_intention)) +
  geom_bar(position = "stack") +
  labs(x="is engaged?", y="Count", fill="Over reported vote") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Proportion of over-reports among nonvoters - no social media vs. social media")
over_report_engaged

# Higher proportions of conservatives and very conservatives over-reported in the data, compared to
# very liberals, liberals, and moderates, but conservative groups also have less total over reporters
```



#### Correlation matrices

```{r}
matrix_independent_vars <- nonvoters %>% 
  dplyr::select(social_media_engagement, 
                 ideo5,
                 education,
                 age,
                 income,
                 White,
                 church_attendance,
                 ideological_strength,
                 political_interest,
                 partisan_strength,
                 married
                 )


matrix <- cor(na.omit(matrix_independent_vars), use = "complete.obs")
corrplot(matrix, method = "color", order = "hclust")

matrix_social_media <- nonvoters %>% 
  dplyr::select(posted_story_link,
         posted_comment,
         saw_story,
         followed_political_event,
         forwarded_story)

matrix_2 <- cor(na.omit(matrix_social_media), use = "complete.obs")
matrix_2
corrplot(matrix_2, method="color", order="hclust")

### Positive correlations - Education and Income, Partisan and Ideological strength, Political interest and SME, Married and Income
### Negative correlations - Church attendance and Partisan strength, Education and age

```



#### Modelling

```{r}
#Convert variables to factors
nonvoters <- nonvoters %>%
  mutate_at(vars(over_reported_intention,
                 active_user,
                 passive_user,
                 posted_story_link,
                 posted_comment,
                 saw_story,
                 followed_political_event,
                 forwarded_story,
                 age_cat,
                 White,
                 Black,
                 other_non_White,
                 female,
                 married,
                 ), as.factor)

```


```{r}
### Create sub-groups

nonvoters_engaged <- nonvoters %>% 
  filter(user_engagement_score != 0)

nonvoters_disengaged <- nonvoters %>% 
  filter(user_engagement_score == 0)

nonvoters_cts <- nonvoters %>% 
  filter(
         ideo5 != 6, 
         faminc_new != 17, 
         church_attendance != 7
         )

nonvoters_cts_engaged <- nonvoters %>% 
  filter(
         user_engagement_score != 0,
         ideo5 != 6, 
         faminc_new != 17, 
         church_attendance != 7
         )

```





#### Hypothesis 1: Political activity on social media is positively associated with over-reporting vote intentions when compared to those who are not active

```{r}

### Politically engaged on social media over past 24 hours
  
model_1 <- glm(over_reported_intention ~ as.factor(is_politically_engaged) +
                 as.factor(education) + 
                 as.factor(income) +
                 Black +
                 other_non_White + 
                 married + 
                 as.factor(church_attendance) +
                 as.factor(age_cat) +
                 as.factor(ideological_strength) + 
                 female + 
                 as.factor(political_interest) 
                 ,
                 data = nonvoters, family = binomial
               )

model_1a <- glm(over_reported_intention ~ as.factor(is_politically_engaged) ,
                 data = nonvoters, family = binomial
                )

model_1_cts<- lm(as.numeric(over_reported_intention) ~ as.factor(is_politically_engaged) 
                        +
                          education +
                 faminc_new +
                 Black +
                 other_non_White +
                 married +
                 church_attendance +
                 age_cat +
                 ideological_strength +
                 female +
                 political_interest 
                 ,
                 data = nonvoters_cts, weights = commonweight
                 )





stargazer(model_1, model_1a, model_1_cts, type="text")
stargazer(model_1_cts, type="text")


```





#### Hypothesis 2: Passive social media users are more likely to over-report their voting intentions than their more active counterparts

```{r}
model_2 <- glm(over_reported_intention ~ as.factor(social_media_engagement) + 
                 education + 
                 income +
                 Black +
                 other_non_White + 
                 married + 
                 church_attendance +
                 age_cat +
                 ideological_strength + 
                 female + 
                 political_interest 
               ,  
               data = nonvoters_engaged, family = binomial
               ) 


model_2a <- glm(over_reported_intention ~ as.factor(social_media_engagement),
               data = nonvoters_engaged, family = binomial
               ) 

model_2_cts <- lm(as.numeric(over_reported_intention) ~ social_media_engagement + 
                 education +
                 faminc_new +
                 Black +
                 other_non_White +
                 married +
                 church_attendance +
                 age_cat +
                 ideological_strength +
                 female +
                 political_interest 
               ,  
               data = nonvoters_cts_engaged, weights = commonweight
               ) 

stargazer(model_2, model_2a, model_2_cts, type="text")

```




#### Robustness check for individual actions on social media

```{r}
model_3 <- glm(over_reported_intention ~ as.factor(saw_story) + as.factor(followed_political_event) + as.factor(posted_story_link) + as.factor(posted_comment) + as.factor(forwarded_story) +
                 education + 
                 income +
                 Black +
                 other_non_White + 
                 married + 
                 church_attendance +
                 age_cat +
                 ideological_strength + 
                 female + 
                 political_interest 
               ,  
               data = nonvoters, family = binomial
               ) 

model_3a <- glm(over_reported_intention ~ as.factor(saw_story) + as.factor(followed_political_event) + 
                  as.factor(posted_story_link) + as.factor(posted_comment) + as.factor(forwarded_story)
               ,  
               data = nonvoters, family = binomial
               ) 

model_3_cts <- lm(as.numeric(over_reported_intention) ~ 
                 as.factor(saw_story) + as.factor(followed_political_event) + 
                 as.factor(posted_story_link) + as.factor(posted_comment) + as.factor(forwarded_story) +
                 education +
                 faminc_new +
                 Black +
                 other_non_White +
                 married +
                 church_attendance +
                 age_cat +
                 ideological_strength +
                 female +
                 political_interest,
               data = nonvoters_cts, weights = commonweight
             ) 

stargazer(model_3, model_3a, model_3_cts, type="text")

```

```{r}
model_4 <- glm(over_reported_intention ~ as.factor(passive_user) + 
                 as.factor(education) + 
                 as.factor(income) +
                 Black +
                 other_non_White + 
                 married + 
                 as.factor(church_attendance) +
                 as.factor(age_cat) +
                 as.factor(ideological_strength) + 
                 female + 
                 as.factor(political_interest)
               ,  
               data = nonvoters_engaged, family = binomial
              
               )


model_4a <- glm(over_reported_intention ~ as.factor(passive_user), 
                data = nonvoters_engaged, family=binomial
                )

model_4_cts <- lm(as.numeric(over_reported_intention) ~ as.factor(passive_user) + 
                 education +
                 faminc_new +
                 Black +
                 other_non_White +
                 married +
                 church_attendance +
                 age_cat +
                 female +
                 ideological_strength +
                 political_interest 
               ,  
               data = nonvoters_cts_engaged, weights = commonweight
               )

stargazer(model_4, model_4a, model_4_cts, type="text")
```

```{r}
model_4_robust <- glm(over_reported_intention ~ as.factor(user_engagement_category) + 
                      education + 
                      income +
                      Black +
                      other_non_White + 
                      married + 
                      church_attendance +
                      age_cat +
                      ideological_strength + 
                      female + 
                      political_interest 
                      ,
                     data = nonvoters_engaged, family = binomial
                
                     )

model_4a_robust <- glm(over_reported_intention ~ as.factor(user_engagement_category) 
                 ,
                 data = nonvoters_engaged, family = binomial
                
                )

model_4_robust_cts <- lm(as.numeric(over_reported_intention) ~ as.factor(user_engagement_category) +
                         education + 
                         faminc_new +
                         Black +
                         other_non_White + 
                         married + 
                         church_attendance +
                         age_cat +
                         ideological_strength + 
                         female + 
                         political_interest 
                         ,
                         data = nonvoters_cts_engaged
                         , weights=commonweight
                         )

stargazer(model_4_robust, model_4a_robust, model_4_robust_cts, type="text")
```





#### Hypothesis 3: Due to the vastness in political opinions between liberals and conservatives in 2020, there will be significant variance in over-reporting behavior between political ideology affiliations

```{r}
model_5 <- glm(over_reported_intention ~ as.factor(social_media_engagement) * as.factor(ideo5) + 
                 education + 
                 income +
                 Black +
                 other_non_White + 
                 married + 
                 church_attendance +
                 age_cat +
                 #ideological_strength + ### commented out due to collinearity with ideo5
                 female + 
                 political_interest
                 ,
                 data = nonvoters_engaged, family = binomial
               )

model_5a <- glm(over_reported_intention ~ as.factor(social_media_engagement) * as.factor(ideo5) 
               ,  
                 data = nonvoters, family = binomial
               )

model_5_cts <- lm(as.numeric(over_reported_intention) ~ social_media_engagement * ideo5 +
                 education +
                 faminc_new + 
                 Black + 
                 other_non_White +
                 married +
                 church_attendance +
                 age_cat +
                 ideological_strength +
                 female +
                 political_interest
                 ,  
                 data = nonvoters_cts_engaged, weights = commonweight
                 )

stargazer(model_5, model_5a, model_5_cts, type="text")
```




#### Output

```{r}
models <- list(model_1, model_2, model_4, model_4_robust, model_5)
models_cts <- list(model_1_cts, model_2_cts, model_4_cts, model_4_robust_cts, model_5_cts)
models_no_covariates <- list(model_1a, model_2a, model_3a, model_4a, model_4a_robust, model_5a)

stargazer(models, type="text")
stargazer(models_cts, type="text")
stargazer(models_no_covariates, type="text")
```




#### Marginal Effects

```{r}
margins_models <- lapply(models, function(x) summary(margins(x)))
margins_no_covariates <- lapply(models_no_covariates, function(x) summary(margins(x)))
margins_cts <- lapply(models_cts, function(x) summary(margins(x)))

for (i in 1:length(margins_models)) {
  print(margins_models[[i]])
}

for (i in 1:length(margins_cts)) {
  print(margins_cts[[i]])
}

for (i in 1:length(margins_no_covariates)) {
  print(margins_no_covariates[[i]])
}
```

#### Robustness 

```{r}

#Running model w/ just controls included
model_robust <- glm(over_reported_intention ~
                 education +
                 income + 
                 Black + 
                 other_non_White +
                 church_attendance +
                 age_cat +
                 female +
                 ideological_strength +
                 political_interest 
                 ,
                 data = nonvoters, family = binomial
                    )

#Replicating dependent variable from Ansolabehere and Hersh 2012 for post-hoc analysis
model_robust_ols <- lm(did_you_vote ~
                 education +
                 income + 
                 Black + 
                 other_non_White +
                 church_attendance +
                 age_cat +
                 female +
                 ideological_strength +
                 political_interest 
                 ,
                 data = nonvoters, weights=commonpostweight
               
                       )


stargazer(model_robust, model_robust_ols, type="text")
stargazer(model_robust, model_robust_ols, type="text")
summary(margins(model_robust_ols))
```

```{r}
model_2_cts_ols <- lm(intend_to_vote ~ social_media_engagement + 
                 education +
                 income +
                 Black +
                 other_non_White +
                 married +
                 church_attendance +
                 age_cat +
                 ideological_strength +
                 female +
                 political_interest 
                 
               ,  
               data = nonvoters_cts_engaged
               
               ) 

model_2a_cts_ols <- lm(intend_to_vote ~ social_media_engagement 
                       ,  
                       data = nonvoters_cts_engaged
               
                       ) 

stargazer(model_2_cts_ols, model_2a_cts_ols, type="text")
```


Article referenced in analysis:

Ansolabehere, S., & Hersh, E. (2012). Validation: What Big Data Reveal About Survey Misreporting and the Real Electorate. Political Analysis, 20(4), 437–459. http://www.jstor.org/stable/23359641

Data used:

Schaffner, Brian; Ansolabehere, Stephen; Luks, Sam, 2021, "Cooperative Election Study Common Content, 2020", https://doi.org/10.7910/DVN/E9N6PH,